Colorado-Pennsylvania Redistricting Comparison

### 2020-12-05 co_pa_comparison.Rmd
Added small intro

>>>>

## Introduction

  Fair elections are a integral part of democracy for without it, the will of the people might not be respected and if that happens we no longer have a democracy. However, despite the huge importance of the elections in the US, there are still ways that a party can negatively impact the election by gaining an unfair advantage. One of the ways that this can happen, is gerrymandering where in order to gain a political advantage in a state by manipulating district boundaries.
